Waving and swaying

### 2014-08-28 Paper/grass.tex
Added spreadsheet with Ghisalberti's Threshold
The threshold Reynolds number with data from Ghisalberti and Nepf (2002) (heneforth GN2002) is calculated to be compared with our results. The data used from table 1 of GN2002 reports the flow rate, the grass height, and water column depth. This data can be converted in terms of our parameters into a scale for velocity U_0. Assuming a turbulent viscosity of 1e-4 m^2/s, gives a Reynolds number for each case. Reynolds numbers below 200 are reported to be stable, while the ones above 200 are reported to be unstable by GN2002. We can plot these Reynol

%\section{Introduction}
Sea grasses exhibit rich set of dynamics due to their interaction with the flow of water and can considerably affect surrounding hydrodynamic conditions.
Resulting changes in hydrodynamic conditions can influence number of environmental variables and processes such as 
transport of sediments, contaminants, dissolved oxygen, plant growth and biomass production etc \cite{Fonseca87,Nepf99}. 
The response of flexible grass canopies to steady current in form of large amplitude coherent oscillation, known as mo-nami \cite{AckermanOkubo93}, plays a central role
in the recruitment of microscopic marine organism such as blue mussel larvae \cite{Grizzle96}. The hydrodynamic mechanism underlying monami is the focus of this paper. 
\newline
Similar phenomenon of large amplitude coherent oscillation of canopy in atmospheric flow known as ho-nami\cite{Inoue56,Raupach96}, have also been observed.
A crucial difference between the atmospheric and aquatic flow is that the atmospheric flows are essentially unbounded vertically\cite{Vivoni98}. Another major
difference between the two is the considerable difference of stiffness of canopies; terrestrial canopies tend to be much more rigid than aquatic canopies\cite{Ghisal02}.
Due to these differences between aquatic and marine flow, our analysis of flow in presence of flexible grass in a bounded domain is applicable only to marine canopies. 
\newline   
Existing explanation of mo-nami invokes the existence of strong shear near the top of the canopy \cite{Ghisal02,Raupach96} due to
different amounts of drag experienced by fluid in and above the canopy. This shear layer is assumed to become unstable to coherent vortices through a mechanism similar to 
Kelvin-Helmholtz instability. Influence of these coherent eddies over sea grasses is manifested in their large amplitude synchronous oscillations.
%Sea grasses exhibit large amplitude wave like motion in response to these eddies propagating downstream.
%are exhibited in form of large amplitude oscillations knows as mo-nami.
\newline
While the shear layer model successfully appears to predict frequency of mo-nami for number of experimental observations, several aspect of existing theory remain unsatisfactory. 
First, linear stability analysis\cite{Raupach96} does not take into account influence of drag due to grass hence is not a self consistent theory. Second, classical free shear flow 
is known to be unstable for all Reynolds number\cite{drazin}, whereas observations\cite{Grizzle96} indicate the existence of a threshold flow speed below which waving is not observed. 
Finally, the thickness of the free shear layer, defined as the momentum thickness of the boundary layer near the grass tip, is in many cases comparable to the unvegetated layer thickness,
 and therefore inconsistent with the assumptions of the free shear layer instability. These drawbacks of existing theory suggest that flow through vegetation requires further investigation for better understanding of the phenomenon.

>>>>

%\section{Introduction}
Sea grasses exhibit rich set of dynamics due to their interaction with the flow of water and can considerably affect surrounding hydrodynamic conditions.
Resulting changes in hydrodynamic conditions can influence number of environmental variables and processes such as 
transport of sediments, contaminants, dissolved oxygen, plant growth and biomass production etc \cite{Fonseca87,Nepf99}. 
The response of flexible grass canopies to steady current in form of large amplitude coherent oscillation, known as mo-nami \cite{AckermanOkubo93}, plays a central role
in the recruitment of microscopic marine organism such as blue mussel larvae \cite{Grizzle96}. The hydrodynamic mechanism underlying monami is the focus of this paper. 
\newline
Similar phenomenon of large amplitude coherent oscillation of canopy in atmospheric flow known as ho-nami\cite{Inoue56,Raupach96}, have also been observed.
A crucial difference between the atmospheric and aquatic flow is that the atmospheric flows are essentially unbounded vertically\cite{Vivoni98,Nepf00}. Another major
difference between the two is the considerable difference of stiffness of canopies; terrestrial canopies tend to be much more rigid than aquatic canopies\cite{Vivoni98,Ghisal02}.
Due to these differences between aquatic and marine flow, our analysis of flow in presence of flexible grass in a bounded domain is applicable only to marine canopies. 
\newline   
Existing explanation of monami invokes the existence of strong shear near the top of the canopy \cite{Ghisal02,Raupach96} due to
different amounts of drag experienced by fluid in and above the canopy. This shear layer is assumed to become unstable to coherent vortices through a mechanism similar to 
Kelvin-Helmholtz instability. Influence of these coherent eddies over sea grasses is manifested in their large amplitude synchronous oscillations.
%Sea grasses exhibit large amplitude wave like motion in response to these eddies propagating downstream.
%are exhibited in form of large amplitude oscillations knows as mo-nami.
\newline
While the shear layer model successfully appears to predict frequency of monami for number of experimental observations, several aspect of existing theory remain unsatisfactory. 
First, linear stability analysis\cite{Raupach96} does not take into account influence of the vegetation and hence is not self consistent. Second, classical free shear flow 
is known to be unstable for all Reynolds number\cite{drazin}, whereas observations\cite{Grizzle96} indicate the existence of a threshold flow speed below which waving is not observed. 
Finally, the thickness of the free shear layer, defined as the momentum thickness of the boundary layer near the grass tip, is in many cases comparable to the unvegetated layer thickness,
 and therefore inconsistent with the assumptions of the free shear layer instability. These drawbacks of existing theory suggest that flow through vegetation requires further investigation for better understanding of the phenomenon.
